---
title: "CPUE analysis report"
lang: en-NZ
format:
  html:
    embed-resources: true
    toc: true
    theme: cosmo
execute:
  echo: false
  warning: false
  message: false
---

Synthetic fisheries workflow. This report is rendered by Quarto from preserved R outputs.

```{r}
# Read preserved results. Report rendering performs no model fitting.
payload <- jsonlite::fromJSON("report-data.json", simplifyVector = FALSE)
result <- payload$result
record <- payload$record
rows_frame <- function(rows) {
  do.call(rbind, lapply(rows, function(row) as.data.frame(row, stringsAsFactors = FALSE)))
}
plot_series <- function(series, field, label) {
  years <- unlist(lapply(series, function(rows) vapply(rows, function(x) x$year, numeric(1))))
  values <- unlist(lapply(series, function(rows) vapply(rows, function(x) x[[field]], numeric(1))))
  colours <- c("#1378a3", "#b56435", "#7357a8", "#328363")
  plot(range(years), range(c(0, values)), type = "n", xlab = "Year", ylab = label)
  for (i in seq_along(series)) {
    lines(vapply(series[[i]], function(x) x$year, numeric(1)),
          vapply(series[[i]], function(x) x[[field]], numeric(1)),
          col = colours[(i - 1) %% length(colours) + 1], lwd = 2)
  }
  legend("topright", names(series), col = colours[seq_along(series)], lty = 1, bty = "n")
}
```
## Methods

Analysis A fits a Poisson GLM in R with year and vessel effects; analysis B uses year effects only. Both include the log of hooks divided by 1000 as an offset. Predictions at fixed effort and reference vessel are scaled to one in the first year. The record filter belongs to analysis A. This report reads the two saved indices.

## Results

```{r}
endpoints <- lapply(names(result$series), function(name) {
  rows <- result$series[[name]]
  list(analysis = name, first_year = rows[[1]]$year,
       final_year = tail(rows, 1)[[1]]$year,
       final_relative_CPUE = tail(rows, 1)[[1]]$index)
})
knitr::kable(rows_frame(endpoints), digits = 3)
plot_series(result$series, "index", "CPUE relative to first year")
```

## Interpretation

Differences between the indices reflect vessel adjustment and the selected records. These synthetic observations illustrate the workflow. The comparison does not validate either index for a real fishery.

## Analysis record

Produced in **`r record$run_id`**. Each input below keeps its original run and output checksum.

```{r}
inputs <- lapply(names(record$inputs), function(key) {
  list(job = key, run = record$inputs[[key]]$run_id,
       output_sha256 = record$inputs[[key]]$checksum)
})
if (length(inputs)) knitr::kable(rows_frame(inputs))
```

New calculations and this Quarto report run inside the declared container. The downloadable bundle includes the actual R job, shared R sources, this QMD, the preserved result JSON, settings and checksums.

```{r}
software <- lapply(names(record$software), function(key) {
  list(component = key, value = as.character(record$software[[key]]))
})
knitr::kable(rows_frame(software))
```

```{r}
#| results: asis
image <- record$software$container
cat("Calculation image and digest: `", image, "`\n\n", sep = "")
if (!is.null(record$software$container_url)) {
  cat("[Container package](", record$software$container_url, ")\n\n", sep = "")
}
if (!is.null(record$source$repository) && !is.null(record$source$commit)) {
  cat("[Recorded source commit](", record$source$repository, "/commit/",
      record$source$commit, ")\n\n", sep = "")
}
cat("<details><summary>Full preserved input record</summary>\n\n```json\n",
    jsonlite::toJSON(record, auto_unbox = TRUE, pretty = TRUE),
    "\n```\n\n</details>\n", sep = "")
```
