---
title: "Surplus-production assessment report"
lang: en-NZ
format:
  html:
    embed-resources: true
    toc: true
    theme: cosmo
execute:
  echo: false
  warning: false
  message: false
---

Synthetic fisheries workflow. This report is rendered by Quarto from preserved R outputs.

```{r}
# Read preserved results. Report rendering performs no model fitting.
payload <- jsonlite::fromJSON("report-data.json", simplifyVector = FALSE)
result <- payload$result
record <- payload$record
rows_frame <- function(rows) {
  do.call(rbind, lapply(rows, function(row) as.data.frame(row, stringsAsFactors = FALSE)))
}
plot_series <- function(series, field, label) {
  years <- unlist(lapply(series, function(rows) vapply(rows, function(x) x$year, numeric(1))))
  values <- unlist(lapply(series, function(rows) vapply(rows, function(x) x[[field]], numeric(1))))
  colours <- c("#1378a3", "#b56435", "#7357a8", "#328363")
  plot(range(years), range(c(0, values)), type = "n", xlab = "Year", ylab = label)
  for (i in seq_along(series)) {
    lines(vapply(series[[i]], function(x) x$year, numeric(1)),
          vapply(series[[i]], function(x) x[[field]], numeric(1)),
          col = colours[(i - 1) %% length(colours) + 1], lwd = 2)
  }
  legend("topright", names(series), col = colours[seq_along(series)], lty = 1, bty = "n")
}
```
## Methods

Four assessment cases combine CPUE indices A and B with two fixed intrinsic growth rates. The annual Schaefer model starts biomass at carrying capacity, subtracts the observed catch and adds surplus production. RTMB constructs the log-index sum-of-squares objective; R's `nlminb` estimates log carrying capacity within explicit bounds, while catchability is profiled. The source records the initial condition, feasible capacity bounds and fit checks. This report reads the fitted results without fitting again.

## Results

```{r}
endpoints <- lapply(names(result$series), function(name) {
  row <- tail(result$series[[name]], 1)[[1]]
  list(case = name, year = row$year, B_over_K = row$B_over_K,
       harvest_rate = row$harvest_rate)
})
knitr::kable(rows_frame(endpoints), digits = 3)
plot_series(result$series, "B_over_K", "Biomass / carrying capacity")
checks <- lapply(result$diagnostics, function(row) {
  list(case = row$case, intrinsic_growth = row$r, biomass_balance_check = row$balance_check, feasibility = row$feasibility_check,
       balance_residual_t = row$balance_residual_t, gradient_check = row$gradient_check,
       projected_gradient = row$projected_gradient_logK, active_bound = row$active_bound,
       boundary_fit = row$boundary_fit, convergence = row$convergence)
})
knitr::kable(rows_frame(checks), digits = 3)
```

## Interpretation

The cases show how CPUE inputs and fixed growth assumptions change the fitted biomass trajectories. Differences between cases are not an uncertainty interval. Inspect boundary fits, optimizer convergence, biomass recurrence and feasibility checks before interpreting a case. The toy model and initial condition provide no stock-management advice.

## Analysis record

Produced in **`r record$run_id`**. Each input below keeps its original run and output checksum.

```{r}
inputs <- lapply(names(record$inputs), function(key) {
  list(job = key, run = record$inputs[[key]]$run_id,
       output_sha256 = record$inputs[[key]]$checksum)
})
if (length(inputs)) knitr::kable(rows_frame(inputs))
```

New calculations and this Quarto report run inside the declared container. The downloadable bundle includes the actual R job, shared R sources, this QMD, the preserved result JSON, settings and checksums.

```{r}
software <- lapply(names(record$software), function(key) {
  list(component = key, value = as.character(record$software[[key]]))
})
knitr::kable(rows_frame(software))
```

```{r}
#| results: asis
image <- record$software$container
cat("Calculation image and digest: `", image, "`\n\n", sep = "")
if (!is.null(record$software$container_url)) {
  cat("[Container package](", record$software$container_url, ")\n\n", sep = "")
}
if (!is.null(record$source$repository) && !is.null(record$source$commit)) {
  commit_url <- paste0(record$source$repository, "/commit/", record$source$commit)
  cat("[", commit_url, "](", commit_url, ")\n\n", sep = "")
}
cat("<details><summary>Full preserved input record</summary>\n\n```json\n",
    jsonlite::toJSON(record, auto_unbox = TRUE, pretty = TRUE),
    "\n```\n\n</details>\n", sep = "")
```
